The discovery of a Higgs boson in 2012 at the Large Hadron Collider and subsequent measurements of its properties represent a major milestone in the understanding of electroweak symmetry breaking. A study of the vector boson scattering provides essential tests that the Higgs mechanism is the sole source of the electroweak symmetry breaking. Additionally, new physics beyond the standard model that alters the quartic gauge couplings or the presence of additional resonances predicts enhancements for amplitudes of the vector boson scattering at high transverse momentum of the vector bosons and high invariant mass of the diboson system.
This thesis reports the first study for the weak vector boson scattering processes with semileptonic final states (WW/WZ/ZZ + jj → lvqq/llqq/vvqq + jj) with data collected by the ATLAS detector during the Run2 of the Large Hadron Collider corresponding to an integrated luminosity of 139 fb
.
The vector boson scattering processes with semileptonic final states are measured with expected significance of * standard deviations, and the fiducial cross-section is measured to be * fb, where stat and syst represent the statistical systematic uncertainties, respectively.
Since the measurement is compatible with the standard model prediction, the results are interpreted in terms of anomalous quartic gauge couplings in the context of the dimension-8 effective field theory. The limits obtained by this thesis are the most stringent to date.
In addition, this thesis achieved several remarkable improvements on the hadronically decaying weak boson identification techniques; the first measurement on the large-R jet energy resolution with the ob- served data; the first development for the machine learning based weak boson identification algorithms; and the first development for the polarization-sensitive large-R jet observable. Those results open new windows to detailed inspections of the vector boson scattering processes at the high invariant mass of the diboson system. Moreover, those results can be applied to other physics analyses using the highly boosted W or Z boson, for example, searches for new physics beyond the standard model with signatures of WW, WZ, and ZZ, and measurements of high-momentum W or Z boson differential cross-sections.

