\chapter*{Acknowledgement}

I would first like to express my gratitude to Gi-Chol Cho, Testuo Deguchi, Minoru Soda, and Koji Terashi for accepting the role of being part of my jury. 
I am grateful for the constructive discussions during the defense and the comments on the manuscript.

I would like to express my gratitude to my supervisor, Takanori Kono, for giving me lots of opportunities and for many supports through the various tasks.

I am grateful to Lydia Fayard, for making my visit possible to the IJCLab and for welcoming me with lots of academic discussions. It was really fortunate for me to have a chance to work with people in the IJCLab group who have great expertise. I would like to express special thanks to Jean-Francois Grivaz, for earnestly helping us to improve the VBS analysis with his expertise.  

Through collaboration on the analysis, I appreciate a lot to the whole VBS team for giving me much advice, and for getting over the problem together. I would like to thank especially the convener, Dimitris Varouchas for giving me lots of advice from the basics, and Antonio Giannini for consulting my tasks.

I would like to deeply thank Takuya Nobe, for his great guidance and help in many aspects of the analysis through countless discussions.

I really appreciate all my colleagues from Ochanomizu University, from the IJCLab,  and from the ATLAS Japan group who worked with me.
It was a great pleasure collaborating with all of them, who made my experience enjoyable. 

I also would like the thank my friends who chatted with me and helped me get through my Ph.D. days.

Finally, I would like to express my biggest thank you to my parents.

  

