\chapter{Systematics uncertainties}
In this section, all systemaatics uncertainties considered in the analysis are described. The uncertainties are deviede into three categories:
Experimental uncertainties, Background modeling uncertainties, Theoretical uncertainties. Each systematics uncertainty is treated as a nuisance parameter as described in Chapter{}. The systematics variations are estimated on the final discriminant described in Chapter{}.

\subsection{Experimental uncertainties}
\begin{table}[!hp]
  \centering
  \footnotesize
  \begin{center}
    \begin{tabular}{|l|l|l|l|}
      \hline
      Source        & Description                     & Analysis Name                                 \\ \hline
      Electrons     & Energy scale                    &  EG\_SCALE\_ALL                               \\
      Electrons     & Energy resolution               &  EG\_RESOLUTION\_ALL                          \\
      Electrons     & Trigger                        &  EL\_EFF\_Trigger\_TOTAL\_1NPCOR\_PLUS\_UNCOR  \\
      Electrons     & ID efficiency SF                &  EL\_EFF\_ID\_TOTAL\_1NPCOR\_PLUS\_UNCOR      \\
      Electrons     & Isolation efficiency SF                &   EL\_EFF\_Iso\_TOTAL\_1NPCOR\_PLUS\_UNCOR   \\
      Electrons     & Reconstruction efficiency SF                &   EL\_EFF\_Reco\_TOTAL\_1NPCOR\_PLUS\_UNCOR   \\ \hline
      Muons         & \pt\ scale                       &   MUONS\_SCALE                                \\
      Muons         & \pt\ scale (charge dependent)          &   MUON\_SAGITTA\_RHO                    \\
      Muons         & \pt\ scale (charge dependent)          &   MUON\_SAGITTA\_RESBIAS                \\
      Muons         & \pt\ resolution MS               &   MUONS\_MS                                   \\
      Muons         & \pt\ resolution ID               &   MUONS\_ID                                   \\
      Muons         & Isolation efficiency SF         &   MUON\_ISO\_SYS                               \\
      Muons         & Isolation efficiency SF         &   MUON\_ISO\_STAT                               \\
      Muons         & Muon reco \& ID efficiency SF               &   MUONS\_EFF\_STAT                  \\
      Muons         & Muon reco \& ID efficiency SF               &   MUONS\_EFF\_STAT\_LOWPT           \\
      Muons         & Muon reco \& ID efficiency SF               &   MUONS\_EFF\_SYST                  \\
      Muons         & Muon reco \& ID efficiency SF               &   MUONS\_EFF\_SYST\_LOWPT           \\
      Muons         & Track-to-vertex association efficiency SF         &   MUON\_TTVA\_SYS             \\
      Muons         & Track-to-vertex association efficiency SF         &   MUON\_TTVA\_STAT            \\ \hline
      MET           & Soft term                       &   MET\_SoftTrk\_ResoPerp                        \\
      MET           & Soft term                       &   MET\_SoftTrk\_ResoPara                        \\
      MET           & Soft term                       &   MET\_SoftTrk\_Scale                           \\ \hline
      \end{tabular}
      \caption{ Qualitative summary of the systematic uncertainties included in this analysis. }
      \label{tab:syst_summary_sources_1}
    \end{center}
  \end{table}

\subsubsection{Quark/Gluon jets uncertainties}
\subsubsection{Modeling uncertainties}
\subsubsection{Reweighting uncertainties}
\subsection{Theoretical uncertainties}
The systematic uncertainties related to the determination or the calculation of the MC.
\subsubsection{Perturbative QCD matrix-element uncertainties}
\begin{itemize}
      \item PDF + $\alpha_s$ uncertainties\\
      Since PDF sets are obtained by fitting experimental dataset, there are uncertainties on selecting different type of PDF sets, which originated from the experimental uncertainties from the dataset and from the choice of the functional form adapted in the PDF fits.
      The uncertainty from the PDF set choice can be assessed by 2 means. One is by calculating the difference within one PDF set by varying its internal parameters, which is called internal PDF uncertainties. The second is from the difference between the nominal sets of different PDF sets, which is called external PDF uncertainties.
      $\alpha_s$ uncertainties are from the experimental uncertainties in the determination of it and the truncated fixed order calculations are used for the calculation.
      \item QCD scale uncertainties\\
      The 
\subsubsection{Parton shower uncertainties}
\subsubsection{NLO order EW corrections}
\end{itemize}
\subsubsection{Small-R jets uncertainties}
\subsubsection{Large-R jet uncertainties}
\subsubsection{B-tagging uncertainties}
The systematic uncertainties associated to the b-tagging.
They are uncertainties on the scaling factor for taking account for the disagreement of the b-tag efficiency between data and MC. Each separated scale factors and corresponding systematic uncertainties are provided for b-,c-, and light-flavor jets from several measurements.
These b-tagging systematic uncertainties are applied when calculating the SF since they are uncertainties on the SF. b-tagging SF is firstly calculated with all small-R jets (PFlowJets) and applied to the events after having selected non b-tagged tagging jets, same as the uncertainties. 



\subsection{NP differently constrained between Asimov and Data fitting}
